---
title: 'Diabetes Project'
author: "Aly O'Mahoney"
date: "10/11/2020"
output:
  rmdformats::readthedown:
    self_contained: true
    lightbox: true
    gallery: false
    highlight: tango
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
if(!require(tidyverse)) install.packages("tidyverse", repos = "http://cran.us.r-project.org")
if(!require(knitr)) install.packages("knitr", repos = "http://cran.us.r-project.org")
if(!require(kableExtra)) install.packages("kableExtra", repos = "http://cran.us.r-project.org")
library(tidyverse)
library(knitr)
library(kableExtra)
```

# Abstract

# Introduction
This report aims to construct a machine learning model which predicts whether a patient is at risk of being diabetic. [Approach 1: Logistic Regression] constricts a logistic regression model. [Approach 2: k-Nearest Neighbours] Constructs a k-nearest neighbours model using the Jaccard distance. [Approach 3: Decision Tree] constructs a decision tree. This method is in line with how people may expect doctors to make decisions in reality. [Approach 4: Random Forest] is an extension on [Approach 3: Decision Tree]. [Ensemble] constructs an ensemble of three of the previous models. [Final Model (Results)] retrains the best performing model on a slightly larger data set and assesses its performance using a validation set which is not used for model construction or selection at any point in this report.

The data being worked with is the [Early stage diabetes risk prediction dataset](https://archive.ics.uci.edu/ml/datasets/Early+stage+diabetes+risk+prediction+dataset.). It was created using questionnaires from the patients of Sylhet Diabetic Hospital (Bangladesh) and has been approved by a doctor [[1](https://archive.ics.uci.edu/ml/datasets/Early+stage+diabetes+risk+prediction+dataset.)]. 

For this report, the Early stage diabetes risk prediction dataset is split into a training and a validation set (`diabetes` and `validation` respectively). Only the `diabetes` data set is used for model construction. The `validation` data set is used only for assessing the performance of the *final* model. `diabetes` is split into `train` and `test`. Various models are constructed using `train` and their performances are assessed using `test`. The best performing model is then retrained using `diabetes` and assessed using `validation`. This way, `validation` has no effect on which model is selected to be the final model. The R code used to construct these data sets, models and plots is available in [this](https://github.com/alyomahoney/Diabetes_Project) GitHub repo.

# Data Exploration
The structure of the `edx` data set is shown below. This section aims to visualise and explore the data being worked with.

```{r loading_data, echo = FALSE}
# at(edx_str, sep = "\n")
```


# Approach 1: Logistic Regression

This section constructs a logistic regression model. The reason logistic regression is used instead of linear regression is that `class` is a binary variable. Therefore, it is appropriate for a model to predict the probability that the `class` of a patient is positive, for example. 




Note that not all factors have the same order

# Approach 2: k-Nearest Neighbours




# Approach 3: Decision Tree




# Approach 4: Random Forest




# Ensemble




# Final Model (Results)




# Conclusion




# References

[1] UCI Machine Learning Repository. *Early stage diabetes risk prediction dataset.* [https://archive.ics.uci.edu/ml/datasets/Early+stage+diabetes+risk+prediction+dataset.](https://archive.ics.uci.edu/ml/datasets/Early+stage+diabetes+risk+prediction+dataset.) (date last accessed - 15/10/2020)

